What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-08-26 paper/main.tex
slightly enlarge text in image

\begin{example}
    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $\lnot p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $\lnot p$, and so on. The lower timeline starts with one step of $\lnot p$ and one step of $p$ outside the grey box, and then enter the infinite run of $\lnot p$ and $p$ repeating.
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}[scale=0.7, transform shape]
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
        \node (m) at ($(p1)!0.5!(p2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};

        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= 1.5cm of m] {\!\!\!$\lnot p$\!\!\!};
        \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= 1cm of p4] {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
        \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);

        \end{tikzpicture}
   %     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
        \caption{Example timeline for specification ``$p$ oscillates every time step''}
        \label{fig:ex2}
    \end{figure}
\end{example}

@@

@@

@@

            \filldraw (287.84bp,8.0bp) -- (287.84bp,60.0bp) -- (357.84bp,60.0bp) -- (357.84bp,8.0bp) -- cycle;

@@

            \draw [->] (54.252bp,34.0bp) .. controls (61.968bp,34.0bp) and (70.673bp,34.0bp)  .. (90.636bp,34.0bp);

@@

            \draw [->] (169.36bp,34.0bp) .. controls (177.45bp,34.0bp) and (185.97bp,34.0bp)  .. (205.41bp,34.0bp);

@@

            \draw [->] (260.25bp,34.0bp) .. controls (267.73bp,34.0bp) and (276.03bp,34.0bp)  .. (295.46bp,34.0bp);

@@

            \filldraw [opacity=1] (322.84bp,34.0bp) ellipse (27.0bp and 18.0bp);

@@

            \draw (322.84bp,34.0bp) node {$\top$};

@@

            \draw (133.61bp,16.05bp) -- (136.05bp,16.15bp) -- (138.47bp,16.3bp) -- (140.85bp,16.49bp) -- (143.18bp,16.74bp) -- (145.46bp,17.03bp) -- (147.68bp,17.36bp) -- (149.83bp,17.75bp) -- (151.9bp,18.18bp) -- (153.88bp,18.65bp) -- (155.76bp,19.16bp) -- (157.54bp,19.71bp) -- (159.22bp,20.31bp) -- (160.78bp,20.94bp) -- (162.23bp,21.61bp) -- (163.56bp,22.31bp) -- (164.76bp,23.04bp) -- (165.83bp,23.8bp) -- (166.78bp,24.59bp) -- (167.59bp,25.41bp) -- (168.28bp,26.25bp) -- (168.83bp,27.11bp) -- (169.25bp,27.99bp) -- (169.55bp,28.89bp) -- (169.72bp,29.8bp) -- (169.76bp,30.72bp) -- (169.69bp,31.65bp) -- (169.5bp,32.59bp) -- (169.19bp,33.53bp) -- (168.77bp,34.47bp) -- (168.25bp,35.41bp) -- (167.63bp,36.35bp) -- (166.92bp,37.28bp) -- (166.11bp,38.2bp) -- (165.22bp,39.11bp) -- (164.26bp,40.01bp) -- (163.21bp,40.89bp) -- (162.1bp,41.75bp) -- (160.93bp,42.59bp) -- (159.7bp,43.41bp) -- (158.42bp,44.2bp) -- (157.09bp,44.96bp) -- (155.71bp,45.69bp) -- (154.3bp,46.39bp) -- (152.85bp,47.06bp) -- (151.38bp,47.69bp) -- (149.87bp,48.29bp) -- (148.35bp,48.84bp) -- (146.8bp,49.35bp) -- (145.24bp,49.82bp) -- (143.66bp,50.25bp) -- (142.07bp,50.64bp) -- (140.47bp,50.97bp) -- (138.86bp,51.26bp) -- (137.24bp,51.51bp) -- (135.62bp,51.7bp) -- (133.99bp,51.85bp) -- (132.37bp,51.95bp) -- (130.74bp,52.0bp) -- (129.11bp,52.0bp) -- (127.48bp,51.95bp) -- (125.85bp,51.85bp) -- (124.22bp,51.7bp) -- (122.6bp,51.51bp) -- (120.99bp,51.26bp) -- (119.38bp,50.97bp) -- (117.78bp,50.64bp) -- (116.19bp,50.25bp) -- (114.61bp,49.82bp) -- (113.04bp,49.35bp) -- (111.5bp,48.84bp) -- (109.97bp,48.29bp) -- (108.47bp,47.69bp) -- (106.99bp,47.06bp) -- (105.54bp,46.39bp) -- (104.13bp,45.69bp) -- (102.76bp,44.96bp) -- (101.43bp,44.2bp) -- (100.14bp,43.41bp) -- (98.91bp,42.59bp) -- (97.74bp,41.75bp) -- (96.63bp,40.89bp) -- (95.59bp,40.01bp) -- (94.62bp,39.11bp) -- (93.73bp,38.2bp) -- (92.92bp,37.28bp) -- (92.21bp,36.35bp) -- (91.59bp,35.41bp) -- (91.07bp,34.47bp) -- (90.65bp,33.53bp) -- (90.35bp,32.59bp) -- (90.15bp,31.65bp) -- (90.08bp,30.72bp) -- (90.12bp,29.8bp) -- (90.29bp,28.89bp) -- (90.59bp,27.99bp) -- (91.01bp,27.11bp) -- (91.57bp,26.25bp) -- (92.25bp,25.41bp) -- (93.07bp,24.59bp) -- (94.01bp,23.8bp) -- (95.09bp,23.04bp) -- (96.29bp,22.31bp) -- (97.61bp,21.61bp) -- (99.06bp,20.94bp) -- (100.62bp,20.31bp) -- (102.3bp,19.71bp) -- (104.08bp,19.16bp) -- (105.97bp,18.65bp) -- (107.95bp,18.18bp) -- (110.01bp,17.75bp) -- (112.16bp,17.36bp) -- (114.38bp,17.03bp) -- (116.66bp,16.74bp) -- (119.0bp,16.49bp) -- (121.38bp,16.3bp) -- (123.79bp,16.15bp) -- (126.23bp,16.05bp) -- (128.69bp,16.0bp) -- (131.15bp,16.0bp) -- cycle;
            \draw (129.92bp,34.0bp) node [align=center] {$\neg \text{a}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

            \draw (232.84bp,34.0bp) ellipse (27.0bp and 18.0bp);
            \draw (232.84bp,34.0bp) node {$\text{a}$};

@@

                        \draw (506.18bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

                        \draw (216.73bp,38.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

                \draw (216.73bp,34.0bp) node [align=center] {$\text{a}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

                \draw (462.49bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

                \draw (142.16bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

                \draw (331.29bp,88.0bp) node [align=center] {$\neg \text{p0} \land \text{p1}$ \\ {\tiny repeats $0$ - $\infty$}};

@@

                \draw (331.29bp,34.0bp) node [align=center] {$\top$ \\ {\tiny repeats $0$ - $\infty$}};

@@

\begin{example}
  Suppose we have a specification ``$p$ oscillates every time step''. It is common to come up with the following two \ltl\ formulas to describe this specification.
  \begin{itemize}
    \item $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$
    \item $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$
  \end{itemize}
  It may be hard, without rigorous analysis, to distinguish which one is correct for the specification. However, our tool can generate the following two timelines for these two formulas as shown in \cref{fig:oscillates1,fig:oscillates2}, which clearly show the first formula is correct and the second formula is equivalent to $\bot$.
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[scale=0.7, transform shape]
  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
  \node (m) at ($(p1)!0.5!(p2)$) {};
  \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};

  \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p4) [right= 1.5cm of m] {\!\!\!$\lnot p$\!\!\!};
  \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p5) [right= 1cm of p4] {\!\!\!$p$\!\!\!};
  \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 4cm of m] {\!\!\!start\!\!\!};
  \draw[thick, line width=1.25] (s) edge[-latex] (p1) (s) edge[-latex] (p3) (p3) edge[-latex] (p2) (p1) edge[-latex] (p4) (p2) edge[-latex] (p4) (p4) edge[-latex] (p5);

  \end{tikzpicture}
%     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$}
  \label{fig:oscillates1}
\end{figure}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[>=latex',line join=bevel, scale=0.7, transform shape]
    \pgfsetlinewidth{1bp}
  %%
  \pgfsetcolor{black}
    % Node: start
  \begin{scope}
    \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
    \pgfsetstrokecolor{strokecol}
    \draw (27.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
    \draw (27.0bp,18.0bp) node {start};
  \end{scope}
  %
  \end{tikzpicture}
  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$)}
  \label{fig:oscillates2}
\end{figure}
\end{example}

>>>>

@@

    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $\lnot p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $\lnot p$, and so on. The lower timeline starts with one step of $\lnot p$ and one step of $p$ outside the grey box, and then enter the infinite run of $\lnot p$ and $p$ repeating.

@@

        \begin{tikzpicture}[>=latex',line join=bevel,scale=0.6, transform shape]

@@

          \filldraw (262.0bp,19.0bp) -- (262.0bp,71.0bp) -- (422.0bp,71.0bp) -- (422.0bp,19.0bp) -- cycle;
          \draw [->] (324.4bp,45.0bp) .. controls (332.06bp,45.0bp) and (340.57bp,45.0bp)  .. (359.62bp,45.0bp);
          \draw [->] (53.503bp,48.868bp) .. controls (83.95bp,53.487bp) and (135.08bp,61.243bp)  .. (180.26bp,68.095bp);
          \draw [->] (52.513bp,38.593bp) .. controls (61.307bp,36.295bp) and (71.403bp,33.656bp)  .. (91.313bp,28.452bp);
          % Edge: 0 -> 3
          \draw [->] (232.05bp,64.622bp) .. controls (241.17bp,61.824bp) and (251.73bp,58.582bp)  .. (271.98bp,52.369bp);
          \draw [->] (144.4bp,20.8bp) .. controls (152.06bp,20.452bp) and (160.57bp,20.065bp)  .. (179.62bp,19.199bp);
          \draw [->] (232.05bp,25.378bp) .. controls (241.17bp,28.176bp) and (251.73bp,31.418bp)  .. (271.98bp,37.631bp);
          \filldraw [opacity=1] (297.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
          \draw (297.0bp,45.0bp) node {$\neg \text{p}$};
          \filldraw [opacity=1] (387.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
          \draw (387.0bp,45.0bp) node {$\text{p}$};
          \draw (27.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
          \draw (27.0bp,45.0bp) node {start};
          \draw (207.0bp,72.0bp) ellipse (27.0bp and 18.0bp);
          \draw (207.0bp,72.0bp) node {$\text{p}$};
          \draw (117.0bp,22.0bp) ellipse (27.0bp and 18.0bp);
          \draw (117.0bp,22.0bp) node {$\neg \text{p}$};
          \draw (207.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
          \draw (207.0bp,18.0bp) node {$\text{p}$};
   %     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
        \caption{Example timeline for specification ``$p$ oscillates every time step''}
        \label{fig:ex2}
        \begin{tikzpicture}[>=latex',line join=bevel,scale=0.6, transform shape]
          \filldraw (301.97bp,8.0bp) -- (301.97bp,60.0bp) -- (371.97bp,60.0bp) -- (371.97bp,8.0bp) -- cycle;

@@

          \draw [->] (54.416bp,34.0bp) .. controls (62.14bp,34.0bp) and (70.893bp,34.0bp)  .. (90.479bp,34.0bp);

@@

          \draw [->] (183.47bp,34.0bp) .. controls (191.95bp,34.0bp) and (200.71bp,34.0bp)  .. (219.63bp,34.0bp);

@@

          \draw [->] (274.37bp,34.0bp) .. controls (282.03bp,34.0bp) and (290.54bp,34.0bp)  .. (309.58bp,34.0bp);

@@

          \filldraw [opacity=1] (336.97bp,34.0bp) ellipse (27.0bp and 18.0bp);

@@

          \draw (336.97bp,34.0bp) node {$\top$};

@@

          \draw (141.33bp,16.05bp) -- (144.21bp,16.15bp) -- (147.06bp,16.3bp) -- (149.87bp,16.49bp) -- (152.62bp,16.74bp) -- (155.31bp,17.03bp) -- (157.93bp,17.36bp) -- (160.46bp,17.75bp) -- (162.9bp,18.18bp) -- (165.23bp,18.65bp) -- (167.46bp,19.16bp) -- (169.56bp,19.71bp) -- (171.54bp,20.31bp) -- (173.38bp,20.94bp) -- (175.08bp,21.61bp) -- (176.65bp,22.31bp) -- (178.06bp,23.04bp) -- (179.33bp,23.8bp) -- (180.45bp,24.59bp) -- (181.41bp,25.41bp) -- (182.21bp,26.25bp) -- (182.87bp,27.11bp) -- (183.37bp,27.99bp) -- (183.72bp,28.89bp) -- (183.92bp,29.8bp) -- (183.97bp,30.72bp) -- (183.88bp,31.65bp) -- (183.65bp,32.59bp) -- (183.29bp,33.53bp) -- (182.8bp,34.47bp) -- (182.19bp,35.41bp) -- (181.46bp,36.35bp) -- (180.61bp,37.28bp) -- (179.66bp,38.2bp) -- (178.61bp,39.11bp) -- (177.47bp,40.01bp) -- (176.24bp,40.89bp) -- (174.93bp,41.75bp) -- (173.55bp,42.59bp) -- (172.1bp,43.41bp) -- (170.59bp,44.2bp) -- (169.02bp,44.96bp) -- (167.4bp,45.69bp) -- (165.73bp,46.39bp) -- (164.03bp,47.06bp) -- (162.28bp,47.69bp) -- (160.51bp,48.29bp) -- (158.71bp,48.84bp) -- (156.89bp,49.35bp) -- (155.04bp,49.82bp) -- (153.18bp,50.25bp) -- (151.31bp,50.64bp) -- (149.42bp,50.97bp) -- (147.52bp,51.26bp) -- (145.62bp,51.51bp) -- (143.7bp,51.7bp) -- (141.79bp,51.85bp) -- (139.87bp,51.95bp) -- (137.95bp,52.0bp) -- (136.02bp,52.0bp) -- (134.1bp,51.95bp) -- (132.18bp,51.85bp) -- (130.27bp,51.7bp) -- (128.35bp,51.51bp) -- (126.45bp,51.26bp) -- (124.55bp,50.97bp) -- (122.66bp,50.64bp) -- (120.79bp,50.25bp) -- (118.93bp,49.82bp) -- (117.08bp,49.35bp) -- (115.26bp,48.84bp) -- (113.46bp,48.29bp) -- (111.68bp,47.69bp) -- (109.94bp,47.06bp) -- (108.24bp,46.39bp) -- (106.57bp,45.69bp) -- (104.95bp,44.96bp) -- (103.38bp,44.2bp) -- (101.87bp,43.41bp) -- (100.42bp,42.59bp) -- (99.03bp,41.75bp) -- (97.73bp,40.89bp) -- (96.5bp,40.01bp) -- (95.35bp,39.11bp) -- (94.31bp,38.2bp) -- (93.36bp,37.28bp) -- (92.51bp,36.35bp) -- (91.78bp,35.41bp) -- (91.17bp,34.47bp) -- (90.68bp,33.53bp) -- (90.32bp,32.59bp) -- (90.09bp,31.65bp) -- (90.0bp,30.72bp) -- (90.05bp,29.8bp) -- (90.25bp,28.89bp) -- (90.6bp,27.99bp) -- (91.1bp,27.11bp) -- (91.76bp,26.25bp) -- (92.56bp,25.41bp) -- (93.52bp,24.59bp) -- (94.64bp,23.8bp) -- (95.91bp,23.04bp) -- (97.32bp,22.31bp) -- (98.88bp,21.61bp) -- (100.59bp,20.94bp) -- (102.43bp,20.31bp) -- (104.41bp,19.71bp) -- (106.51bp,19.16bp) -- (108.74bp,18.65bp) -- (111.07bp,18.18bp) -- (113.51bp,17.75bp) -- (116.04bp,17.36bp) -- (118.66bp,17.03bp) -- (121.35bp,16.74bp) -- (124.1bp,16.49bp) -- (126.91bp,16.3bp) -- (129.76bp,16.15bp) -- (132.64bp,16.05bp) -- (135.53bp,16.0bp) -- (138.44bp,16.0bp) -- cycle;
          \draw (136.98bp,34.0bp) node [align=center] {$\neg \text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

          \draw (246.97bp,34.0bp) ellipse (27.0bp and 18.0bp);
          \draw (246.97bp,34.0bp) node {$\text{a}$};

@@

                        \draw (506.18bp,34.0bp) node [align=center] {$\text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

                        \draw (216.73bp,38.0bp) node [align=center] {$\text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

                \draw (216.73bp,34.0bp) node [align=center] {$\text{a}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

                \draw (462.49bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

                \draw (142.16bp,34.0bp) node [align=center] {$\neg \text{a} \lor \neg \text{b}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

                \draw (331.29bp,88.0bp) node [align=center] {$\neg \text{p0} \land \text{p1}$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

                \draw (331.29bp,34.0bp) node [align=center] {$\top$ \\ {\small \emph{repeats $0$ - $\infty$}}};

@@

  Suppose we have a specification ``$p$ oscillates every time step''. It is common to come up with the following two \ltl\ formulas to describe this specification.
  \begin{itemize}
    \item $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$
    \item $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$
  \end{itemize}
  It may be hard, without rigorous analysis, to distinguish which one is correct for the specification. However, our tool can generate the following two timelines for these two formulas as shown in \cref{fig:oscillates1,fig:oscillates2}, which clearly show the first formula is correct and the second formula is equivalent to $\bot$.
  \begin{tikzpicture}[>=latex',line join=bevel,scale=0.6, transform shape]
    \filldraw (262.0bp,19.0bp) -- (262.0bp,71.0bp) -- (422.0bp,71.0bp) -- (422.0bp,19.0bp) -- cycle;
    \draw [->] (324.4bp,45.0bp) .. controls (332.06bp,45.0bp) and (340.57bp,45.0bp)  .. (359.62bp,45.0bp);
    \draw [->] (53.503bp,48.868bp) .. controls (83.95bp,53.487bp) and (135.08bp,61.243bp)  .. (180.26bp,68.095bp);
    \draw [->] (52.513bp,38.593bp) .. controls (61.307bp,36.295bp) and (71.403bp,33.656bp)  .. (91.313bp,28.452bp);
    % Edge: 0 -> 3
    \draw [->] (232.05bp,64.622bp) .. controls (241.17bp,61.824bp) and (251.73bp,58.582bp)  .. (271.98bp,52.369bp);
    \draw [->] (144.4bp,20.8bp) .. controls (152.06bp,20.452bp) and (160.57bp,20.065bp)  .. (179.62bp,19.199bp);
    \draw [->] (232.05bp,25.378bp) .. controls (241.17bp,28.176bp) and (251.73bp,31.418bp)  .. (271.98bp,37.631bp);
    \filldraw [opacity=1] (297.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
    \draw (297.0bp,45.0bp) node {$\neg \text{p}$};
    \filldraw [opacity=1] (387.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
    \draw (387.0bp,45.0bp) node {$\text{p}$};
    \draw (27.0bp,45.0bp) ellipse (27.0bp and 18.0bp);
    \draw (27.0bp,45.0bp) node {start};
    \draw (207.0bp,72.0bp) ellipse (27.0bp and 18.0bp);
    \draw (207.0bp,72.0bp) node {$\text{p}$};
    \draw (117.0bp,22.0bp) ellipse (27.0bp and 18.0bp);
    \draw (117.0bp,22.0bp) node {$\neg \text{p}$};
    \draw (207.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
    \draw (207.0bp,18.0bp) node {$\text{p}$};
%     \includegraphics[scale=0.4]{examples/ex2/ex2.png}
  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \lor ((\lnot p) \land \nextt p))$}
  \label{fig:oscillates1}
    \draw (27.0bp,18.0bp) ellipse (27.0bp and 18.0bp);
    \draw (27.0bp,18.0bp) node {start};
  \caption{Timeline for $\always ((p \land \nextt (\lnot p)) \land ((\lnot p) \land \nextt p))$ (a single ``start'' means every time step is $\bot$)}
  \label{fig:oscillates2}
